Looking for a Signal in the Noise: Revisiting Obesity and the microbiome

### 2016-03-18 Sze_ObesityMicrobiomeMetaNoMetaHit_PeerJ_2016.Rmd
power calc add to paper

```{r install_needed_packages, echo=FALSE, message=FALSE, warning=FALSE}
deps = c("knitr","vegan","epiR","AUCRF","meta","metafor","ggplot2", "plyr", "reshape2", "RColorBrewer", "scales", "gridExtra");
for (dep in deps){
  if (dep %in% installed.packages()[,"Package"] == FALSE){
    install.packages(as.character(dep), quiet=TRUE);
  }
  library(dep, verbose=FALSE, character.only=TRUE)
}

@@

**Table 4. Summary of Power Calculations for each Individual for Shannon Diversity and B/F ratio for Non-obese versus Obese**

@@

Study <- as.character(PowerTable$Study)
PowerH <- PowerTable$StudyPowerH
PowerBF <- PowerTable$StudyPowerBF

table4 <- cbind(Study, PowerH, PowerBF)
colnames(table4) <- c("Study", "Shannon Diversity Power (%)", "B/F Ratio Power (%)")

>>>>

```{r install_needed_packages, echo=FALSE, message=FALSE, warning=FALSE}
deps = c("knitr","vegan","epiR","AUCRF","meta","metafor","ggplot2", "plyr", "reshape2", "RColorBrewer", "scales", "gridExtra", "pwr", "statmod");
for (dep in deps){
  if (dep %in% installed.packages()[,"Package"] == FALSE){
    install.packages(as.character(dep), quiet=TRUE);
  }
  library(dep, verbose=FALSE, character.only=TRUE)
}

@@

**Table 4. Summary of Power Calculations for Shannon Diversity and B/F ratio for Non-obese versus Obese**

@@

Study <- c(as.character(PowerTable$Study), "COMBINED")
keep <- which(group.data.test$obese=="Yes")
CombinedH <- pwr.t2n.test(d=mean(group.data.test$ZH[-keep])-mean(group.data.test$ZH[keep]), n1=length(group.data.test$ZH[-keep]), n2=length(group.data.test$ZH[keep]))
CombinedBF <- pwr.t2n.test(d=mean(group.data.test$ZLogBF[-keep])-mean(group.data.test$ZLogBF[keep]), n1=length(group.data.test$ZLogBF[-keep]), n2=length(group.data.test$ZLogBF[keep]))

set.seed(3)
CombinedHRR <- power.fisher.test(
  sum(ShannonRRTable$tposH)/
        (sum(ShannonRRTable$tposH)+sum(ShannonRRTable$tnegH)), 
  sum(ShannonRRTable$cposH)/
    (sum(ShannonRRTable$cposH)+sum(ShannonRRTable$cnegH)), 
  sum(ShannonRRTable$tposH)+sum(ShannonRRTable$tnegH), sum(ShannonRRTable$cposH)+sum(ShannonRRTable$cnegH), 
  alpha=0.05, nsim=1000, alternative="two.sided")*100

set.seed(3)
CombinedBFRR <- power.fisher.test(
  sum(BFRatioRRTable$tposBF)/
        (sum(BFRatioRRTable$tposBF)+sum(BFRatioRRTable$tnegBF)), 
  sum(BFRatioRRTable$cposBF)/
    (sum(BFRatioRRTable$cposBF)+sum(BFRatioRRTable$cnegBF)), 
  sum(BFRatioRRTable$tposBF)+sum(BFRatioRRTable$tnegBF), sum(BFRatioRRTable$cposBF)+sum(BFRatioRRTable$cnegBF), 
  alpha=0.05, nsim=1000, alternative="two.sided")*100

PowerH <- c(PowerTable$StudyPowerH, format(round(CombinedH$power*100, 1), nsmall=1))
PowerHRR <- c(PowerTable$StudyPowerHRR, CombinedHRR)
PowerBF <- c(PowerTable$StudyPowerBF, format(round(CombinedBF$power*100, 1), nsmall=1))
PowerBFRR <-c(PowerTable$StudyPowerBFRR, CombinedBFRR)

table4 <- cbind(Study, PowerH, PowerHRR, PowerBF, PowerBFRR)
colnames(table4) <- c("Study", "Shannon Diversity Power (%)", "Shannon RR Power (%)", "B/F Ratio Power (%)", "B/F ratio RR (%)")
